Current State of Knowledge Representation Systems for Robotics

### 2011-11-24 krs-survey.tex
Could not find much from Bielefeld...?

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMKRF & & Suh et al. \par (Hanyang Univ.) & & & & & \cite{Suh2007} \\
DY-KNOW & & Heintz, Dowerty \par (Linköping Univ.) & & & & & \cite{Heintz2004} \\
 & & Wrighteagle \\
 & & Vincze \\
 & & (Bielfeld Univ.) \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

@@

\begin{tabular}{ll}
\hiderowcolors
{\bf Project} & {\bf Common-sense knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
DY-KNOW & \\
OMKRF & \\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
(Bielfeld) & \\
ARMAR &  \\
Hertzberg (Osnabrück) & \\
(DFKI Bremen) & \\
(JSK) & \\

>>>>

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMKRF & & Suh et al. \par (Hanyang Univ.) & & & & & \cite{Suh2007} \\
DY-KNOW & & Heintz, Dowerty \par (Linköping Univ.) & & & & & \cite{Heintz2004} \\
 & & Wrighteagle \\
 & & Vincze \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

\fxfatal{Bielefeld -> could not find much...}
\fxfatal{Kollar/Tellex -> really focusing on the natural language grounding}

@@

\begin{tabular}{ll}
\hiderowcolors
{\bf Project} & {\bf Common-sense knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
DY-KNOW & \\
OMKRF & \\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg (Osnabrück) & \\
(DFKI Bremen) & \\
(JSK) & \\
